### 2023-02-06 definitions.tex
Cleaned up some

\begin{remark} 
$k$-resilienc $\leq$ bounded Resilience 
%	$\leq$ Resilience.  
\textcolor{red}{oui si strong monootony, non ? sinon}
\end{remark}

@@

Since Reset Petri nets are also effective WSTS with strong monotony, we could think to use the undecidability of LTL for Reset Petri nets.

and with effective basis of $post^*$ ???

% \alain{cette dernière propriété fait penser à la $t$-liveness dans un rdPetri ou n'importe quel modèle monotone..qui peut s'exprimer par $ ~ \forall s' \in S ~ (s \rightarrow^* s') \implies \exists s'' \in U_t ~ s' \rightarrow^{*} s''$ ? avec $U_t=\uparrow \pred(t)$=la clôture par le haut des préconditions pour déclencher la transition $t$}

expliquer toutes les variantes de la résilience

% \textcolor{red}{In the Özkan paper the input include a basis of $\uparrow post^*(s)$. Not $100$\% sure it is necessary, think we can try to do without this assumption in the input.}

Let $(X,\leq)$ be a wqo and $U$ be an upward closed subset of $X$. We say that $U$ is \emph{computable} if there is an algorithm that computes a finite basis of $U$.

@@

\begin{theorem}
In WSTS with strong monotony, 
the {\sc bounded resilience} problem
is equivalent to the
{\sc resilience} problem.
\end{theorem}

>>>>

@@

% Since Reset Petri nets are also effective WSTS with strong monotony, we could think to use the undecidability of LTL for Reset Petri nets.

% and with effective basis of $post^*$ ???

% expliquer toutes les variantes de la résilience

% Let $(X,\leq)$ be a wqo and $U$ be an upward closed subset of $X$. We say that $U$ is \emph{computable} if there is an algorithm that computes a finite basis of $U$.

@@

\begin{proposition}
In WSTS with strong monotony, the bounded resilience problem is
reducible to the $k$-resilience problem.
\end{proposition}

\begin{proof}
strong WSTS
$\pred^*(I) = \pred^{k}(I)$
Check all $k$ until $\pred^*(I) = \pred^{k}(I)$.
\end{proof}

\begin{proposition}
In WSTS with strong monotony, the bounded resilience problem is
equivalent to the resilience problem.
\end{proposition}
